Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-20 2017-Xudong-SMT/OpenPNets-SMT.tex
Update figure
CCS and LOTOS example figure in section 2.
Adjust the size and font.
Add the introduction for section 5
Add the introduction for section 5.

\begin{minipage}{6cm}
  \includegraphics[width=\linewidth]{XFIG/CCS1}
  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
\end{minipage}
\hspace{2mm}
\begin{minipage}{6cm}
  \includegraphics[width=\linewidth]{XFIG/Enable1}
  \\[1.3ex]
  \includegraphics[width=\linewidth]{XFIG/Enable2}
  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
\end{minipage}

@@

\section{Implementation}

\TODO{Xudong: Missing a general summary before going into details. You
  can get inspiration from the following (reasonnable level of
  abstraction):}
\ERIC{
=> Context = use the existing software architecture from VCE (ref to \cite{FASE} paper)\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignements\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
}

>>>>

\begin{minipage}{7cm}
  \includegraphics[width=\linewidth]{XFIG/CCS1}
  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
\end{minipage}
\hspace{2mm}
\begin{minipage}{5cm}
  \includegraphics[width=\linewidth]{XFIG/Enable1.eps}
  \\[1.3ex]
  \includegraphics[width=\linewidth]{XFIG/Enable2.eps}
  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
\end{minipage}

@@

\section{Implementation}
\QIN{
VerCors platform uses pNet as the intermediate language for some language or graphical formalism to be translated into both input for a checker and for generating code automatically to ease the specification from non-expert users\cite{FASE}, compiling it from those language or graphical formalism in the pNet API. We compute the open automaton of an open pNet also in that pNet API directly implementing the sketch showed before. However, we made some modification, merging the step 2a-2b and applying Tr2 with the premisses from subnets to generate open transitions, application of Tr1 is still conducted in a simple way. At same time, we apply the fresh function to rename all the variable to make them unique and readable. Besides that, we also have a management of assignments throughout the whole computation. Satisfiability check is done only at top level of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations. But the submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.
}

\TODO{Xudong: Missing a general summary before going into details. You
  can get inspiration from the following (reasonable level of
  abstraction):}

\ERIC{
=> Context = use the existing software architecture from VCE (ref to \cite{FASE} paper)\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitly constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignments\\
=> Satisfiability check is done only at top level of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
}
